%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Senior Systems Engineer} % Job title
    {EPAM Systems} % Organization
    {Sofia, Bulgaria} % Location
    {Apr. 2025 - } % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Configure continuous integration and deployment.}
        \item {Develop and maintain configuration management for the whole infrastructure.}
        \item {Develop and maintain infrastructure as a code.}
        \item {Provide operational support for the whole infrastructure and automation tools.}
        \item {Ensure that any technical issues faced by project teams are resolved.}
        \item {Communicate effectively to all the stakeholders and team members.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {DevOps Engineer 2} % Job title
    {Quickbase} % Organization
    {Sofia, Bulgaria} % Location
    {Mar. 2022 - Feb. 2025} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Deployed and managed applications on \textbf{Google Cloud Platform (GCP)} using \textbf{CloudRun}, ensuring scalable and efficient serverless execution.}
        \item {Automated CI/CD pipelines using \textbf{TeamCity} and \textbf{GitHub Actions} to streamline code delivery and deployment processes.}
        \item {Implemented infrastructure as code (IaC) with \textbf{Terraform} and \textbf{Terragrunt} to provision and manage cloud resources efficiently.}
        \item {Containerized applications using \textbf{Docker} and orchestrated deployments with Kubernetes for optimized scaling and management.}
        \item {Developed custom automation scripts in \textbf{Python} for system management, integration tasks, and infrastructure automation.}
        \item {Worked closely with cross-functional teams to optimize infrastructure performance and ensure the availability of critical services.}
        \item {Monitored and maintained system health, identifying and resolving performance bottlenecks to improve reliability.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Senior DevOps Engineer (Financial Times Sofia)} % Job title
    {Musala Soft} % Organization
    {Sofia, Bulgaria} % Location
    {Jul. 2020 - Feb. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Managed AWS Datalake solutions for handling large-scale data storage and processing.}
        \item {Implemented and maintained \textbf{Apache Airflow} for orchestrating complex data pipelines and workflows.}
        \item {Orchestrated containerized applications using \textbf{Kubernetes}, ensuring high availability and scalability.}
        \item {Automated deployment processes and workflows using \textbf{CircleCI}, ensuring continuous integration and delivery.}
        \item {Utilized \textbf{Helm} for managing Kubernetes applications and simplifying deployment configurations.}
        \item {Provisioned and configured infrastructure using \textbf{Ansible} for automation and infrastructure as code (IaC).}
        \item {Worked closely with development teams to ensure streamlined deployments and optimized infrastructure performance.}
        \item {Monitored and maintained system performance, troubleshooting complex issues to ensure seamless operations.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Senior DevOps Engineer} % Job title
    {Musala Soft} % Organization
    {Sofia, Bulgaria} % Location
    {Dec. 2019 - Jul. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Managed and maintained container orchestration environments using Docker Swarm and OpenShift for large-scale application deployments.}
        \item {Automated continuous integration and delivery pipelines using GitLab CI to streamline software delivery and testing.}
        \item {Provisioned and maintained RedHat Linux environments for various applications, ensuring high availability and performance.}
        \item {Collaborated with development and operations teams to optimize infrastructure for scalability and cost-efficiency.}
        \item {Implemented infrastructure as code (IaC) using tools like Ansible and Terraform to automate provisioning and configuration management.}
        \item {Provided support for troubleshooting and resolving complex infrastructure and deployment issues.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Computer Systems Administrator \& DevOps Engineer, DevOps Consultant Specialist} % Job title
    {Optimalbit LLC} % Organization
    {Mink, Belarus (Remote)} % Location
    {Nov. 2018 - Jul. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Managed system infrastructure and deployment pipelines from old monolith applications to cloud based ones.}
        \item {Implemented and maintained CI/CD workflows to streamline software delivery and testing using Jenkins, Selenium Unittesting.}
        \item {Automated server provisioning, configuration management, and monitoring using tools like Chef, Ansible, Terraform and Packer.}
        \item {Ensured system security through regular updates, firewalls, and access control policies.}
        \item {Collaborated with development teams to optimize infrastructure for scalability and performance.}
        \item {Saved over 30\% of the overall AWS costs by establishing a quarterly purchasing strategiy for RI (Reserved Instance) and SP (Savings Plan).}
        \item {Provided technical support and troubleshooting for systems, servers, and cloud environments.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {System Admin \& DevOps} % Job title
    {EMPIREDEV LLC} % Organization
    {Miami, Florida, US (Remote)} % Location
    {Nov. 2017 - Nov. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Managed system infrastructure and deployment pipelines for old monolith applications.}
        \item {Implemented and maintained CI/CD workflows to streamline software delivery and testing.}
        \item {Automated server provisioning, configuration management, and monitoring using tools like Chef and Vagrant.}
        \item {Ensured system security through regular updates, firewalls, and access control policies.}
        \item {Collaborated with development teams to optimize infrastructure for scalability and performance.}
        \item {Provided technical support and troubleshooting for systems and servers}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Systems administrator} % Job title
    {REGIONAL STATISTICS OFFICE} % Organization
    {Holguin, Cuba} % Location
    {Sep. 2014 - Sep. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Managed and maintained the infrastructure and services for the Province's Regional Statistics Office, ensuring optimal system performance, security, and reliability.}
        \item {Responsible for overseeing server management, network configuration, and user support across all regional operations.}
        \item {Coordinated the installation, configuration, and troubleshooting of hardware and software systems.}
        \item {Implemented best practices for data backup, recovery, and security.}
        \item {Ensured seamless operations by proactively addressing system issues and providing technical support to staff and developers.}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
